### 2017-03-31 paper/intro.tex
pass on text

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development\Mar{Fan Long
  (http://people.csail.mit.edu/fanl/) often uses a plot to show the
  exponential rise of projects in github.  Please check if you can
  find a reference to that or ask Fan Long what source he used (maybe
  browsed with public API).} and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows.

\begin{enumerate}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Speedups of parallelization.}
\item \textbf{Issues versus benefits on using parallelization modes.}
\end{enumerate}

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain time
costly test suites.  In the limit, parallelization will be fruitless
if all projects contain short-running test suites. The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  This dimension
is concerned with popularity of parallelization.  The third aspect
evaluates the observed impact of parallelization on cost.  Finally,
the last dimension evaluates the issues and benefits associated with
running test suites with different parallel configurations (/modes).
Overall, the study of these dimensions help us layout the current
state-of-the-practice about the use and impact of parallelization in open-source
projects, which presumably do not have large budgets.

>>>>

%% \Mar{Fan Long
%%   (http://people.csail.mit.edu/fanl/) often uses a plot to show the
%%   exponential rise of projects in github.  Please check if you can
%%   find a reference to that or ask Fan Long what source he used (maybe
%%   browsed with public API).}

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows.

\begin{enumerate}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Prevalence of test suite parallelization.}
\item \textbf{Developer's opinion (when parallelization not used).}    
\item \textbf{Speedups of parallelization (when used).}
\item \textbf{Issues versus benefits on using parallelization modes.}
\end{enumerate}

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain costly
test suites.  In the limit, parallelization would be fruitless if all
projects contained short-running test suites. The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  The third
dimension evaluates how developers involved in costly projects not
using test suite parallelization perceive this technology.  The fourth
dimension evaluates the observed impact of parallelization (when
actually used) on cost.  Finally, the fifth dimension evaluates the
issues and benefits associated with running test suites with different
parallel configurations (/modes).  Overall, this study help us layout
the current state-of-the-practice about usage and impact of test suite
parallelization in open-source projects.
